Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-13 tex/paper.tex
Add figure 5 caption

\begin{figure*}
  \makebox[\textwidth][c]{\includegraphics[scale=0.72]{misclassify}}
  \caption{This is a tiger. Rawr!}
  \label{fig:misclassify}
\end{figure*}

>>>>

\begin{figure*}
  \makebox[\textwidth][c]{\includegraphics[scale=0.72]{misclassify}}
  \caption{The left side shows examples of correctly classified digits by the one convolutional/pooling layer architecture, while the left side shows examples of incorrectly
  classified digits by the same architecture. The top right corner shows the correct label. The numbers below the image are the first and second place labels determined by the
  CNN. Note how the miscalssified images can be seen to resemble the network's chosen label. The number 8 was misclassified multiple times, likely due to its similarlity to other
  digits when deformed from its canonical form.}
  \label{fig:misclassify}
\end{figure*}
